### 2016-03-25 paper1.tex
All figures on top of page.
All tables on top of page, rotated some of them.
Chapter intro-->background and using footnotes in titles

\chapter{Detection of Low-Mass-ratio Stellar Binary Systems}
\label{chap:pilot}
We now turn back to the variant of the direct spectral detection method originally discussed in Chapter \ref{chap:dsd}, in which the targets are very early-type, rapidly-rotating stars. This chapter was previously published \citep{Gullikson2013_2}. The co-author, Sarah Dodson-Robinson, was my advisor at the time and provided much of the idea for the project.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig1.pdf}
  \caption{This figure illustrates the approximate flux ratio limit to
  the detection method outlined in section
  \ref{paper1_sec:newmethod}. \emph{Top panel}: Residuals after telluric
  correction (see section \ref{paper1_sec:reduction}) for chip 2 of HIP 80582 are in black, with an
  atmosphere model for an $0.9 M_{\odot}$ star at 50.1 Myr below it in
  red. The flux ratio at this age is $F_s/F_p = 0.0092$. \emph{Middle panel}: The scaled model
  spectrum was added to the telluric residuals, and then the sum was
  cross-correlated with the model. Despite the signal being
  significantly below the noise level, the star was detected at a high
significance. The y axis, in units of the standard deviation of the
cross-correlation function, shows that the significance of the peak is over
$4\sigma$. \emph{Bottom panel}: Same as the middle panel, but the
model spectrum was added to the residuals with a 50 km s$^{-1}$ velocity
offset.}
  \label{paper1_fig:method}
\end{figure*}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig2.pdf}
  \caption{\emph{Top panel}: The telluric spectrum (absorption due to Earth's
    atmosphere) in the wavelength range from $2290-2400$ nm. Most of the lines are
    from CH$_4$, with a few H$_2$O lines appearing in the right
    half. \emph{Bottom panel}: The model spectrum of a 5500 K star
    with $\log (g) = 4.0$ and solar metallicity. Note that the line density of telluric
    lines is comparable to or greater than that of the star model, and many of the
    telluric lines are stronger than the stellar lines.}
  \label{paper1_fig:telluric}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig3.pdf}
  \caption{The telluric correction steps for chip three of CRIRES
    wavelength setting $\lambda_{ref} = 2329.3$ nm. \emph{Top panel:}
    Normalized spectrum (black), with the best-fit telluric model
    (red). \emph{Middle panel:} Residuals after dividing the observed
    spectrum by the telluric model. Note the large spikes near
    $2328.5$, $2331$, and $2335$ nm. \emph{Bottom panel:} Correction
    after fitting the large residuals to Gaussians. }
  \label{correctionsteps}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig4.pdf}
  \caption{Cross-correlation for HIP 26713, using a 5600 K star model spectrum as template. The y-axis is in units of
    the standard deviation of the cross-correlation function. The peak is very near the maximum velocity of $|v_\mathrm{max}| = 256$ km s$^{-1}$, assuming a circular orbit (see equation \ref{paper1_eqn:vmax}). The likelihood of observing the system nearly edge on and at a quadrature point, so that $|v| \sim |v_\mathrm{max}|$, is $p \approx 0.01$. However, it is possible that the system has an eccentric orbit, effectively increasing $|v_\mathrm{max}|$.}
  \label{paper1_fig:hip26713}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=5.7in]{Figures/paper1_fig5.pdf}
  \caption{Cross-correlations for HIP 92855, for all dates observed. A 6100 K star model spectrum is used as the template for each cross-correlation. The y-axis is in units of
    the standard deviation of the cross-correlation function. A single strong peak is seen in the
    cross-correlations from 2007 May 9, 2007 August 2, 2008 September
    19, and 2008 October 10. The reasonably strong peak on 2007 June 9 is identified
  as probably arising from imperfect telluric line removal or random noise, since it
  has $v>v_\mathrm{max}$ given by equation \ref{paper1_eqn:vmax}.}
  \label{paper1_fig:hip92855}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=5.5in]{Figures/paper1_fig6.pdf}
  \caption{Completeness diagram for the full sample of main-sequence B
  stars, split up by the effective temperature of the secondary
  star. The points correspond to the individual stars in the sample,
  and their sizes reflect the signal-to-noise ratio in the
  spectrum. Note that the signal-to-noise is calculated after the
  telluric line removal, and counts any telluric residuals as
  noise. The figures are also color-coded by the fraction of trials
  that detected the companion (see section
  \ref{paper1_sec:completeness}). Contours are drawn to guide the eye. The red 
  areas in each plot indicate the regions for which our sample is complete.}
  \label{paper1_fig:completeness}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig7.pdf}
  \caption{Estimates of the binary fraction of B0-B5 stars,
    as a function of binary mass-ratio. This work found no unambiguous companions,
    and so we give $90\%$ upper limits (solid black line). $90\%$
    upper limits are also given assuming that HIP 92855 is a real
    binary system (dotted black line). The upper limits are only different within the
    $1\sigma$ error bars on the mass-ratio for HIP 92855. The nearly flat 
    distribution found by \cite{Sana2012} is shown as the dashed red line. The average binary 
    fraction found by \cite{Evans2011} is also shown (dash-dot blue line). The
    \cite{Evans2011} value is a \emph{lower} limit and an average over all mass-ratios from $0.1 < q < 0.3$, but they estimate
    that their sample is very complete, and so the true multiplicity fraction is quite close to their value.}
  \label{paper1_fig:limits}
\end{figure*}

@@

%\begin{center}
\begin{small}
\begin{longtable}{|cccccc|}
    %\tablecaption{Full star sample}
    %\tablefirsthead{\hline Star & Spectral Type & Age (Myr) & Distance
      %(pc) & Maximum Separation (AU) \\ \hline}

@@

        \label{paper1_tab:sample}
\end{longtable}
\end{small}
%\end{center}

\newpage
%\begin{center}
   \begin{longtable}{|cccc|}
      \caption{Summary of adjusted line strengths. The units of line
        strength are cm$^{-1}$/(molecule $\times$ cm$^{-2}$)} \\
        \hline
        Wavelength (nm) & Molecule & Old Strength & New Strength \\ \hline \hline
        \endfirsthead

@@

%\begin{center}
 \begin{small}
   \begin{longtable}{|ccp{6cm}|}
      \caption{Summary of Cross-Correlation Function Peak Rejection Steps. See Section \ref{paper1_sec:results} for more information} \\
        \hline
        Step  & Description & Method \\ \hline
        \endfirsthead

@@

    \label{paper1_tab:rejection}
  \end{longtable}
 \end{small}
%\end{center}

>>>>

\chapter{Detection of Low-Mass-ratio Stellar Binary Systems\footnote{
  This chapter was previously published \citep{Gullikson2013_2}. The co-author, Sarah Dodson-Robinson, was my advisor at the time and provided much of the idea for the project.
}}
\label{chap:pilot}
We now turn back to the variant of the direct spectral detection method originally discussed in Chapter \ref{chap:dsd}, in which the targets are very early-type, rapidly-rotating stars.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig1.pdf}
  \caption{This figure illustrates the approximate flux ratio limit to
  the detection method outlined in section
  \ref{paper1_sec:newmethod}. \emph{Top panel}: Residuals after telluric
  correction (see section \ref{paper1_sec:reduction}) for chip 2 of HIP 80582 are in black, with an
  atmosphere model for an $0.9 M_{\odot}$ star at 50.1 Myr below it in
  red. The flux ratio at this age is $F_s/F_p = 0.0092$. \emph{Middle panel}: The scaled model
  spectrum was added to the telluric residuals, and then the sum was
  cross-correlated with the model. Despite the signal being
  significantly below the noise level, the star was detected at a high
significance. The y axis, in units of the standard deviation of the
cross-correlation function, shows that the significance of the peak is over
$4\sigma$. \emph{Bottom panel}: Same as the middle panel, but the
model spectrum was added to the residuals with a 50 km s$^{-1}$ velocity
offset.}
  \label{paper1_fig:method}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig2.pdf}
  \caption{\emph{Top panel}: The telluric spectrum (absorption due to Earth's
    atmosphere) in the wavelength range from $2290-2400$ nm. Most of the lines are
    from CH$_4$, with a few H$_2$O lines appearing in the right
    half. \emph{Bottom panel}: The model spectrum of a 5500 K star
    with $\log (g) = 4.0$ and solar metallicity. Note that the line density of telluric
    lines is comparable to or greater than that of the star model, and many of the
    telluric lines are stronger than the stellar lines.}
  \label{paper1_fig:telluric}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig3.pdf}
  \caption{The telluric correction steps for chip three of CRIRES
    wavelength setting $\lambda_{ref} = 2329.3$ nm. \emph{Top panel:}
    Normalized spectrum (black), with the best-fit telluric model
    (red). \emph{Middle panel:} Residuals after dividing the observed
    spectrum by the telluric model. Note the large spikes near
    $2328.5$, $2331$, and $2335$ nm. \emph{Bottom panel:} Correction
    after fitting the large residuals to Gaussians. }
  \label{correctionsteps}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig4.pdf}
  \caption{Cross-correlation for HIP 26713, using a 5600 K star model spectrum as template. The y-axis is in units of
    the standard deviation of the cross-correlation function. The peak is very near the maximum velocity of $|v_\mathrm{max}| = 256$ km s$^{-1}$, assuming a circular orbit (see equation \ref{paper1_eqn:vmax}). The likelihood of observing the system nearly edge on and at a quadrature point, so that $|v| \sim |v_\mathrm{max}|$, is $p \approx 0.01$. However, it is possible that the system has an eccentric orbit, effectively increasing $|v_\mathrm{max}|$.}
  \label{paper1_fig:hip26713}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=5.7in]{Figures/paper1_fig5.pdf}
  \caption{Cross-correlations for HIP 92855, for all dates observed. A 6100 K star model spectrum is used as the template for each cross-correlation. The y-axis is in units of
    the standard deviation of the cross-correlation function. A single strong peak is seen in the
    cross-correlations from 2007 May 9, 2007 August 2, 2008 September
    19, and 2008 October 10. The reasonably strong peak on 2007 June 9 is identified
  as probably arising from imperfect telluric line removal or random noise, since it
  has $v>v_\mathrm{max}$ given by equation \ref{paper1_eqn:vmax}.}
  \label{paper1_fig:hip92855}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=5.5in]{Figures/paper1_fig6.pdf}
  \caption{Completeness diagram for the full sample of main-sequence B
  stars, split up by the effective temperature of the secondary
  star. The points correspond to the individual stars in the sample,
  and their sizes reflect the signal-to-noise ratio in the
  spectrum. Note that the signal-to-noise is calculated after the
  telluric line removal, and counts any telluric residuals as
  noise. The figures are also color-coded by the fraction of trials
  that detected the companion (see section
  \ref{paper1_sec:completeness}). Contours are drawn to guide the eye. The red 
  areas in each plot indicate the regions for which our sample is complete.}
  \label{paper1_fig:completeness}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig7.pdf}
  \caption{Estimates of the binary fraction of B0-B5 stars,
    as a function of binary mass-ratio. This work found no unambiguous companions,
    and so we give $90\%$ upper limits (solid black line). $90\%$
    upper limits are also given assuming that HIP 92855 is a real
    binary system (dotted black line). The upper limits are only different within the
    $1\sigma$ error bars on the mass-ratio for HIP 92855. The nearly flat 
    distribution found by \cite{Sana2012} is shown as the dashed red line. The average binary 
    fraction found by \cite{Evans2011} is also shown (dash-dot blue line). The
    \cite{Evans2011} value is a \emph{lower} limit and an average over all mass-ratios from $0.1 < q < 0.3$, but they estimate
    that their sample is very complete, and so the true multiplicity fraction is quite close to their value.}
  \label{paper1_fig:limits}
\end{figure}

@@

%\begin{center}
\clearpage
\afterpage{%
\begin{small}
\begin{longtable}{|cccccc|}
    %\tablecaption{Full star sample}
    %\tablefirsthead{\hline Star & Spectral Type & Age (Myr) & Distance
      %(pc) & Maximum Separation (AU) \\ \hline}

@@

        \label{paper1_tab:sample}
\end{longtable}
\end{small}
}
%\end{center}

\clearpage
\newpage
%\begin{center}
   \begin{longtable}{|cccc|}
      \caption{Summary of adjusted line strengths. The units of line
        strength are cm$^{-1}$/(molecule $\times$ cm$^{-2}$)} \\
        \hline
        Wavelength (nm) & Molecule & Old Strength & New Strength \\ \hline \hline
        \endfirsthead

@@

%\begin{center}
\clearpage
 \begin{small}
   \begin{longtable}{|ccp{6cm}|}
      \caption{Summary of Cross-Correlation Function Peak Rejection Steps. See Section \ref{paper1_sec:results} for more information \label{paper1_tab:rejection}} \\
        \hline
        Step  & Description & Method \\ \hline
        \endfirsthead

@@

  \end{longtable}
 \end{small}

### 2016-03-25 paper2.tex
All figures on top of page.
All tables on top of page, rotated some of them.
Chapter intro-->background and using footnotes in titles

\chapter{Future Direct Spectroscopic Detection of Hot Jupiters with IGRINS}
\label{chap:hotjup}
Several authors have used a variant of the method we described in  Chapter \ref{chap:psi1dra} to search for emission from ``Hot Jupiter`` planets orbiting a sun-like star. In this case the flux ratio is much more extreme, but still possible with enough high signal-to-noise ratio spectra. In this chapter, we generate simulations of the IGRINS instrument to assess whether it can detect Hot Jupiter emission. This chapter was previously published \citep{Gullikson2013}. The co-author, Mike Endl, was my co-supervisor at the time and provided much of the inspiration for the work as well as a great deal of technical assistance. While the instrument was being built at the time of publication, it is now functioning on the 2.7m telescope at McDonald Observatory and a pilot survey based on this work is in progress.

@@

\begin{table}
  \centering
    \caption{Physical properties of the HD 189733 and HD 209458 planetary systems. The effective temperatures, masses, and radii are from \cite{Torres2008}, and r (the ratio of the flux in an average spectral line to the flux in the continuum for the planet) are from the model spectra used in this work (See Figure \ref{paper2_fig:modelcomp} and the discussion before Equation \ref{paper2_eqn:snrcrit}).}
  \begin{tabular}{|c|ccccc|}
    \hline
    Star & $T_\mathrm{ eff, star}$ (K) & $T_\mathrm{ eff, planet}$ (K) & M$_\mathrm{ p}$ (M$_\mathrm{ Jup}$) & R$_\mathrm{ p}$ (R$_\mathrm{ Jup}$)  & $r$ \\ \hline
    HD 189733 & 5040 & 1200 & 1.14 & 1.138 & 0.77 \\
    HD 209458 & 6065 & 1450 & 0.69 & 1.359 & 0.90 \\ \hline
  \end{tabular}

  \label{paper2_tab:planet}
\end{table}

\begin{table}
  \centering
  \caption{Summary of minimum S/N ratios needed to detect planets for our test cases. Efficient heat redistribution refers to observations where the dayside and nightside temperatures are the same, while inefficient heat redistribution is when the nightside temperature is half that of the dayside temperature. The model dependence is estimated by using different planet models to cross-correlate against the same observation (see section \ref{paper2_sec:results}). We do not attempt to simulate observations with S/N $>1500$ because such a high value would be very difficult to achieve in the near-infrared.}
  \begin{tabular}{|c|ccc|}
    \hline
    Star & Planet Model for CCF & Heat Redistribution & Critical S/N Ratio \\ \hline
    HD 189733 & HD 189733b & efficient & 200 \\
    HD 189733 & HD 189733b & inefficient & 450 \\
    HD 189733 & HD 209458b & efficient & 300 \\
    HD 189733 & HD 209458b & inefficient & 800 \\
    HD 209458 & HD 209458b & efficient & 900 \\
    HD 209458 & HD 209458b & inefficient & 1200 \\
    HD 209458 & HD 189733b & efficient & 1200 \\
    HD 209458 & HD 189733b & inefficient & $>$1500 \\ \hline
  \end{tabular}
  \label{paper2_tab:snrcrit}
\end{table}

\begin{center}
\begin{longtable}{|ccccc|}

\caption{Estimated exposure times required for correctly retrieving the true masses of Hot Jupiters. The times are for a single observation; roughly 20-25 observations of the system at different phases are necessary to detect the planet. See Section \ref{paper2_sec:results} for the calculation of the flux ratio and critical S/N.} \\
\hline
Star Name & $ \mathrm{K_s}$ Magnitude & K-band flux ratio & S/N required & Time Required (Minutes) \\ \hline
\endfirsthead

@@

\label{paper2_tab:targetlist}
\end{longtable}
\end{center}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=6.5in]{Figures/paper2_fig1.pdf}
  \caption{Telluric Correction process. \emph{Top Panel}: Original
    science star spectrum for a segment in the water band on the blue side of the K band.  \emph{Middle Panel}: Telluric residuals
    after the model fit. The science star residuals are in the upper (solid) line, and
    the standard star residuals are in the lower (dashed) line. The systematic errors we introduced appear like emission lines in both spectra. \emph{Bottom Panel}:
    Result after division of the science star residuals by the
    standard star residuals. The telluric contamination has largely been removed.}
  \label{paper2_fig:tellcorr}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=6.5in]{Figures/paper2_fig2.pdf}
  \caption{\emph{Top Panel}: Individual cross-correlation functions for simulations of HD 189733 with an average S/N = 500, and with complete heat redistribution. The velocities are shifted at each orbital phase such that the cross-correlation function should have a peak at 0 km s$^{-1}$; the planet is only detected in a few of the observations. \emph{Bottom panel}: The total cross-correlation function, after adding the cross-correlation functions for each individual observation. Here the planet is very clearly detected with $6.29 \sigma$ significance.}
  \label{paper2_fig:allcorr}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=5.5in]{Figures/paper2_fig3.pdf}
  \caption{A comparison of the HD189733 planet model with the HD209458
  planet model. The gap in the middle is is in between the H and K
  spectral windows, where water absorption in the Earth's atmosphere
  blocks most of the incoming light. HD209458b has a thermal inversion
  in its atmosphere, which generates the emission lines near 1950
  nm. HD189733 b is somewhat cooler and has more water, giving its
  spectrum stronger spectral lines.}
  \label{paper2_fig:modelcomp}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=6.5in]{Figures/paper2_fig4.pdf}
  \caption{A summary of the significance of the point at 0 km s$^{-1}$ in the total cross-correlation functions for each of the mass-ratio guesses, for a series of observations of HD 189733 with an average S/N = 500 and complete heat redistribution (the same as in Figure \ref{paper2_fig:allcorr}). The peak in this figure determines the planet to star mass-ratio, and therefore the true planet mass. The width of the peak $1 \sigma$ below its maximum determines the uncertainty in the planet mass.}
  \label{paper2_fig:massratio}
\end{figure}

>>>>

\chapter{Future Direct Spectroscopic Detection of Hot Jupiters with IGRINS\footnote{
    This chapter was previously published \citep{Gullikson2013}. The co-author, Mike Endl, was my co-supervisor at the time and provided much of the inspiration for the work as well as a great deal of technical assistance.
}}
\label{chap:hotjup}
Several authors have used a variant of the method we described in  Chapter \ref{chap:psi1dra} to search for emission from ``Hot Jupiter`` planets orbiting a sun-like star. In this case the flux ratio is much more extreme, but still possible with enough high signal-to-noise ratio spectra. In this chapter, we generate simulations of the IGRINS instrument to assess whether it can detect Hot Jupiter emission.  While the instrument was being built at the time of publication, it is now functioning on the 2.7m telescope at McDonald Observatory and a pilot survey based on this work is in progress.

@@

\clearpage
\afterpage{%
\begin{table}
  \centering
    \caption{Physical properties of the HD 189733 and HD 209458 planetary systems. The effective temperatures, masses, and radii are from \cite{Torres2008}, and r (the ratio of the flux in an average spectral line to the flux in the continuum for the planet) are from the model spectra used in this work (See Figure \ref{paper2_fig:modelcomp} and the discussion before Equation \ref{paper2_eqn:snrcrit}).}
  \begin{tabular}{|c|ccccc|}
    \hline
    Star & $T_\mathrm{ eff, star}$ (K) & $T_\mathrm{ eff, planet}$ (K) & M$_\mathrm{ p}$ (M$_\mathrm{ Jup}$) & R$_\mathrm{ p}$ (R$_\mathrm{ Jup}$)  & $r$ \\ \hline
    HD 189733 & 5040 & 1200 & 1.14 & 1.138 & 0.77 \\
    HD 209458 & 6065 & 1450 & 0.69 & 1.359 & 0.90 \\ \hline
  \end{tabular}

  \label{paper2_tab:planet}
\end{table}
}

\clearpage
\begin{table}
  \centering
  \caption{Summary of minimum S/N ratios needed to detect planets for our test cases. Efficient heat redistribution refers to observations where the dayside and nightside temperatures are the same, while inefficient heat redistribution is when the nightside temperature is half that of the dayside temperature. The model dependence is estimated by using different planet models to cross-correlate against the same observation (see section \ref{paper2_sec:results}). We do not attempt to simulate observations with S/N $>1500$ because such a high value would be very difficult to achieve in the near-infrared.}
  \begin{tabular}{|c|ccc|}
    \hline
    Star & Planet Model for CCF & Heat Redistribution & Critical S/N Ratio \\ \hline
    HD 189733 & HD 189733b & efficient & 200 \\
    HD 189733 & HD 189733b & inefficient & 450 \\
    HD 189733 & HD 209458b & efficient & 300 \\
    HD 189733 & HD 209458b & inefficient & 800 \\
    HD 209458 & HD 209458b & efficient & 900 \\
    HD 209458 & HD 209458b & inefficient & 1200 \\
    HD 209458 & HD 189733b & efficient & 1200 \\
    HD 209458 & HD 189733b & inefficient & $>$1500 \\ \hline
  \end{tabular}
  \label{paper2_tab:snrcrit}
\end{table}

\clearpage
\newpage
\begin{center}
\begin{longtable}{|ccccc|}

\caption{Estimated exposure times required for correctly retrieving the true masses of Hot Jupiters. The times are for a single observation; roughly 20-25 observations of the system at different phases are necessary to detect the planet. See Section \ref{paper2_sec:results} for the calculation of the flux ratio and critical S/N. \label{paper2_tab:targetlist}} \\
\hline
Star Name & $ \mathrm{K_s}$ Magnitude & K-band flux ratio & S/N required & Time Required (Minutes) \\ \hline
\endfirsthead

@@

\end{longtable}
\end{center}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=6.5in]{Figures/paper2_fig1.pdf}
  \caption{Telluric Correction process. \emph{Top Panel}: Original
    science star spectrum for a segment in the water band on the blue side of the K band.  \emph{Middle Panel}: Telluric residuals
    after the model fit. The science star residuals are in the upper (solid) line, and
    the standard star residuals are in the lower (dashed) line. The systematic errors we introduced appear like emission lines in both spectra. \emph{Bottom Panel}:
    Result after division of the science star residuals by the
    standard star residuals. The telluric contamination has largely been removed.}
  \label{paper2_fig:tellcorr}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=6.5in]{Figures/paper2_fig2.pdf}
  \caption{\emph{Top Panel}: Individual cross-correlation functions for simulations of HD 189733 with an average S/N = 500, and with complete heat redistribution. The velocities are shifted at each orbital phase such that the cross-correlation function should have a peak at 0 km s$^{-1}$; the planet is only detected in a few of the observations. \emph{Bottom panel}: The total cross-correlation function, after adding the cross-correlation functions for each individual observation. Here the planet is very clearly detected with $6.29 \sigma$ significance.}
  \label{paper2_fig:allcorr}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=5.5in]{Figures/paper2_fig3.pdf}
  \caption{A comparison of the HD189733 planet model with the HD209458
  planet model. The gap in the middle is is in between the H and K
  spectral windows, where water absorption in the Earth's atmosphere
  blocks most of the incoming light. HD209458b has a thermal inversion
  in its atmosphere, which generates the emission lines near 1950
  nm. HD189733 b is somewhat cooler and has more water, giving its
  spectrum stronger spectral lines.}
  \label{paper2_fig:modelcomp}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=6.5in]{Figures/paper2_fig4.pdf}
  \caption{A summary of the significance of the point at 0 km s$^{-1}$ in the total cross-correlation functions for each of the mass-ratio guesses, for a series of observations of HD 189733 with an average S/N = 500 and complete heat redistribution (the same as in Figure \ref{paper2_fig:allcorr}). The peak in this figure determines the planet to star mass-ratio, and therefore the true planet mass. The width of the peak $1 \sigma$ below its maximum determines the uncertainty in the planet mass.}
  \label{paper2_fig:massratio}
\end{figure}
